Dissertation

### 2024-10-12 Manuscript/pre_sections/acknowledgements.qmd
update acknowledgements

First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly limitless patience, clear thinking, and unwavering guidance. His ability to effortlessly demonstrate the power of so many tools has been awe-inspiring, and I am forever thankful for his mentorship. I also extend my heartfelt thanks to Dr. Rob Nosofsky for his sharp questions and encouragement of model-based thinking, and to Dr. Peter Todd for being a constant source of encouragement.

My foundation in psychological science was laid at the University of Wisconsin-Madison. I am indebted to Dr. Shawn Green, who took a chance on me despite my mediocre grades and lack of experience, introducing me to the world of psychological research. Special thanks to Aaron Cochrane for answering my countless questions, introducing me to R, and advanced data analysis techniques.

I am grateful for the camaraderie and intellectual stimulation provided by my friends at Indiana University, particularly those in the Geolab and Psychology department. Johnathan Avery, Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others have been integral to my graduate school experience. A special mention goes to Jack Avery for introducing me to rock climbing and engaging in fun conversations that often led to unexpected ideas.

The teachers at Pardeeville High School played an essential role in nurturing my curiosity and establishing the educational foundation that shaped my early learning. The professors at UW-Madison and Indiana University further cultivated that curiosity, profoundly influencing my academic development.

I would also like to extend my heartfelt thanks to my family. My parents, Mary and Jim Gorman, have always been a source of love and unwavering belief in my abilities. My brother, Joseph, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed. Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.

>>>>

First, I owe immense appreciation to my advisor, Rob Goldstone, for his clear thinking and unwavering support, patiently guiding me throughout my dissertation journey. His demonstration of how a single scientist can contribute meaningful work across several distinct areas has been truly awe-inspiring.

I also extend my heartfelt thanks to Rob Nosofsky, who always asked sharp questions that challenged my thinking and encouraged model-based approaches, and to Peter Todd, whose encouragement and enthusiasm played an especially important role during the final stages of my work.

My journey into the study of the mind began at the Learning and Transfer Lab at the University of Wisconsin-Madison, where I am forever indebted to Dr. Shawn Green. He gave me my first research job despite my total lack of experience, and through his guidance, I discovered my passion for research. It was my time in his lab that made it clear to me that pursuing a career in psychological research was what I wanted to do. I also want to thank Aaron Cochrane for investing significant time in answering my many questions, introducing me to R, and humoring my naïve inquiries into advanced data analysis and statistics.

The camaraderie, friendship, and intellectual stimulation I received from my friends at Indiana University have been vital to my graduate school experience. I am particularly grateful to Johnathan Avery, who introduced me to bouldering and joined me in bouncing unexpected ideas around in our fun conversations. I also want to thank Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others from the Geolab and Psychology department. Their support made long hours in front of the computer screen more enjoyable and productive.

I owe much to my teachers at Pardeeville High School for laying the foundation of my education and to the professors at UW-Madison and Indiana University, who continued to foster and build upon that foundation. Their dedication helped to instill in me a love of learning and a drive to pursue knowledge that has lasted throughout my academic journey.

I would also like to extend my heartfelt thanks to my family. My parents, Mary and Jim Gorman, have been my unwavering pillars of support. My brother, Joseph Gorman, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed. Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.

### 2024-10-12 Manuscript/pre_sections/pre_html2.qmd
update acknowledgements

<style>
    body {
        font-family: Times, "Times New Roman", serif;
        line-height: 1.6;
    }
    .title {
        text-align: center;
        margin-top: 50px;
        font-size: 24px;
        font-weight: bold;
    }
    .author {
        text-align: center;
        margin-top: 300px;
        font-size: 32px;
    }
    .submitted {
        text-align: center;
        margin-top: 200px;
        font-size: 16px;
    }
    .date {
        text-align: center;
        margin-top: 200px;
        font-size: 16px;
    }
    .committee {
        text-align: center;
        margin-top: 150px;
        font-size: 16px;
        width: 60%;
        margin-left: auto;
        margin-right: auto;
    }
    .signature {
        display: flex;
        justify-content: space-between;
        margin-top: 50px;
    }
    .signature div {
        width: 45%;
        text-align: center;
    }
    .copyright {
        text-align: center;
        margin-top: 300px;
        font-size: 16px;
        margin-bottom: 200px;
        }
</style>

>>>>

<style>
    body {
        font-family: Times, "Times New Roman", serif;
        line-height: 1.6;
    }
    .title {
        text-align: center;
        margin-top: 50px;
        font-size: 24px;
        font-weight: bold;
    }
    .author {
        text-align: center;
        margin-top: 300px;
        font-size: 21px;
    }
    .submitted {
        text-align: center;
        margin-top: 200px;
        font-size: 16px;
    }
    .date {
        text-align: center;
        margin-top: 200px;
        font-size: 16px;
    }
    .committee {
        text-align: center;
        margin-top: 150px;
        font-size: 16px;
        width: 60%;
        margin-left: auto;
        margin-right: auto;
    }
    .signature {
        display: flex;
        justify-content: space-between;
        margin-top: 50px;
    }
    .signature div {
        width: 45%;
        text-align: center;
    }
    .copyright {
        text-align: center;
        margin-top: 300px;
        font-size: 16px;
        margin-bottom: 500px;
        }
</style>
